
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

We apply molecular simulation to predict the equilibrium structure of organic molecular aggregates and how these structures determine material properties, with a focus on software engineering practices for ensuring correctness.
Because simulations are implemented in software, there is potential for authentic scientific reproducibility in such work: An entire experimental apparatus (codebase) can be given to another investigator who should be able to use the same processes to find the same answers.
Yet in practice, there are many barriers which stand in the way of reproducible molecular simulations that we address through automation, generalization, and software packaging. 
Collaboration on and application of the  Molecular Simulation and Design Framework (MoSDeF) features prominently.

We present structural investigations of organic molecule aggregates and the development of infrastructure and workflows that help manage, initialize, and analyze molecular simulation results through the following scientific applications:
First principles density functional theory (DFT) study of cyanine dye dimers to observe excitonic splitting with comparison to experiment.
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes using DFT.
A perspective on the ecosystem around molecular simulation, specifically training, community, and tools.
A cataloguing of the energetic contributions of para-substituents to the crystal structure of diphenylurea molecules using DFT.
A screening study where we validate that the self-assembled poly-3-hexylthiophene (P3HT) morphologies show the same state dependency as in prior work using a different model.
And finally, a multi-university collaborative reproducibility study where we examine modeling choices that give rise to differences between simulation engines.
In aggregate, we reinforce need for pipelines and practices emphasizing transferability, reproducibility, useability, and extensibility in molecular simulation.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "BSUmain"
%%% End: 
